A performance assessment of evolutionary algorithms in volunteer computing environments: the importance of entropy

### 2016-11-14 EvoPar2017/paper.Rnw
SoA
The SPACE framework

Several authors have already described system using JavaScript  either
for unwitting
\cite{unwitting-ec,boldrin2007distributed} or volunteer 
\cite{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\cite{duda2013distributed,DBLP:journals/corr/abs-0801-1210,EvoStar2014:jsEO}. Most
of these papers focused on testing the system by itself as proofs of
concepts, more than on its performance or their actual influence on
the result of an evolutionary algorithm. In fact, some of them do not
even work in as a distributed computing system
\cite{EvoStar2014:jsEO}, describing the expressive capabilities of
JavaScript for evolutionary computation.

>>>>

Several authors have already described systems using JavaScript  either
for unwitting
\cite{unwitting-ec,boldrin2007distributed} or volunteer 
\cite{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\cite{duda2013distributed,DBLP:journals/corr/abs-0801-1210,EvoStar2014:jsEO}.

Using a peer to peer approach, the SPACE framework \cite{Leclerc2016} distributes fitness 
evaluations across a heterogeneous pool of cloud compute nodes and volunteer
peer computers running a browser. In SPACE peers stablis a bi-directional 
communication with the server using the Socket.io JavaScript library.  
As an experiment they provide an ASM.js compiled version of the RoboGen 
software platform, showing that JavaScript can be used in a broad 
spectrum of applications.

Most
of these papers focused on testing the system by itself as proofs of
concepts, more than on its performance or their actual influence on
the result of an evolutionary algorithm. In fact, some of them do not
even work in as a distributed computing system
\cite{EvoStar2014:jsEO}, describing the expressive capabilities of
JavaScript for evolutionary computation.
